### 2023-03-11 article3.qmd
update

The biological carbon pump (BCP) refers to a series of processes that transport biogenic carbon produced in sunlit surface waters to the ocean interior [@Claustre2021-tx]. It is composed of three main pathways [@Claustre2021-tx; @Boyd2019-ez; @Siegel2022-wd]: the biological gravitational pump that is the gravitational settling of particulate organic carbon (POC); the physically mediated particle injection pump that represents physical mechanisms that transport dissolved organic carbon (DOC) to depth via mixing processes; and the biologically mediated particle injection pump that characterizes the transport of POC (and DOC) by diel and seasonal migration of animals in the water column. Historically, the BCP was mainly studied with sediment traps [@Honjo2008-kn] and Thorium-234 radionuclide disequilibria [@Buesseler2007-ql] focused on the gravitational pump hence the contribution of DOC and migrating animals to the BCP was likely under-estimated. However, the advent of autonomous underwater vehicles (AUVs) equipped with a variety of physical and biogeochemical sensors have demonstrated their ability to better understand the latter [e.g. @Omand2015-mf; @DallOlmo2016-ex; @Llort2018-pa; @Lacour2019-id; @Haentjens2020-dc; @Stukel2017-lc]. Still, we are missing processes to close the carbon budget [@Giering2014-tj; @Boyd2019-ez] and unkowns remain in the under-sampled mesopelagic (i.e. twilight) zone [@Martin2020-wa]. In order to fill the observational gaps, the Biogeochemical-Argo (BGC-Argo) network aims to develop an operational global array of 1000 profiling floats measuring six core variables from the surface to 2000 m [@Claustre2020-jo]: oxygen, nitrate, pH, chlorophyll a (Chla), suspended particles ($b_{bp}$) and downwelling irradiance. In addition to the six core variables, new sensors have been developped to target specific BCP-related questions [@Claustre2020-jo; @Claustre2021-tx; @Chai2020-uq]. In this study, we will focus on BGC-Argo floats equipped with two new sensors: the Underwater Vision Profiler (UVP6) [@Picheral2021-sx] and a transmissometer used as an optical sediment trap (OST).

The UVP6 is a low power miniaturized version of the UVP5 [@Picheral2010-to]. It consists of an underwater camera that counts particles and images objects in, respectively, the 0.1 - 2.5 cm and 0.8 - 2.5 cm size range. The latest version of the UVP6 also embarks an embedded image classification algorithm that transmits the abundance of 20 classes in near-real time. The OST consists of a vertically mounted transmissometer whose upward-facing optical window intercepts sinking particles. The latter have already been used on AUVs [@Bishop2004-at; @Bishop2009-ka; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk].

Two pairs of BGC-Argo floats equipped with both the UVP6 and an OST were deployed in the southern part of the Labrador Sea in May 2022 to investigate seasonal and bloom-related particle and carbon fluxes. The Labrador and the northern part the atlantic are charateterid by blablabla -\> lire le truc et faire la micro revie sur l'atlantique nord, son bloom et la mer du labrador.

but it is the first time that BGC-Argo floats are deployed with both a UVP6 and an OST.

In this work, we will

-   Pour l'intro je dois lire briggs 2011-2020

-   projet remocean Hervé

-   miwing convection virginie thierry?

-   atlantic nord, le bloom de l'atlantic nord

-   léo lacour

-   yashayeav

-   hanetjens 2020

introduire la notion de cycle de flotteurs BGC-Argo etc (+ parking depth)

-   dire que le but du papier est de faire une comparaison OST UVP qui sont deux instruments qui permettent de mesurer la meme chose (le flux des particules, l'abondance de particules) et donc le flux de carbone de manière indirecte papier GRL Lacour de 2015
-   introduire le POC ici et introduire la BCP vite fait (classique)
-   dire que Chla = proxy pour phyto biomass
-   BGC-Argo floats are pseudo-lagrangian platforms
-   si on peut prouver que le diagramme ST, les massses d'eau sont les memes, alors on peut peut-être parler des ratios entre particlues à 500 et 1000 m
-   définir la méthode de calcul de la MLD
-   plotter la MLD sur les profils verticaux de
-   from llort 2017: This is especially true in the Southern Ocean, where the circulation has been described as equivalent barotropic (Gille et al., 2007; Killworth & Hughes, 2002). An equivalent barotropic circulation basically implies that the strength of the current might change with depth (weaker as depth increases) but the orientation does not change. Therefore, Argo and BGCArgo can be interpreted as "quasi-Lagrangian" because floats follow well ocean mesoscale circulation lasting more than 1 week; yet they cannot follow shorter and smaller features such the ones associated to submesocale circulation

Two pairs of Biogeochemical-Argo (BGC) floats were planned to be deployed at the time of the annual spring bloom in the Labrador Sea (LS). The latter is characterized by two bioregions with distinct phytoplankton bloom phelonogies on both side of the 60°N parallel [@Lacour2015-da]. The northern part is characterized by a short spring bloom in late April whereas the bloom in the southern part starts in April-May and slowly develops to reach its maximum in June [@Lacour2015-da]. In this study, two pairs of floats were deployed south of the 60°N parallel with a first couple (WMO 6904240 and 4903634) deployed closely to it (58.9°N) in late May 2022.

@@

>>>>

The biological carbon pump (BCP) refers to a series of processes that transport biogenic carbon produced in sunlit surface waters to the ocean interior [@Claustre2021-tx]. It is composed of three main pathways [@Claustre2021-tx; @Boyd2019-ez; @Siegel2022-wd]: the biological gravitational pump that is the gravitational settling of particulate organic carbon (POC); the physically mediated particle injection pump that represents physical mechanisms that transport dissolved organic carbon (DOC) to depth via mixing processes; and the biologically mediated particle injection pump that characterizes the transport of POC (and DOC) by diel and seasonal migration of animals in the water column. Historically, the BCP was mainly studied with sediment traps [@Honjo2008-kn] and Thorium-234 radionuclide disequilibria [@Buesseler2007-ql] focused on the gravitational pump hence the contribution of DOC and migrating animals to the BCP was poorly known. However, the advent of autonomous underwater vehicles (AUVs) equipped with a variety of physical and biogeochemical sensors have demonstrated their ability to better understand them [e.g. @Omand2015-mf; @DallOlmo2016-ex; @Llort2018-pa; @Lacour2019-id; @Haentjens2020-dc; @Stukel2017-lc]. Still, we are missing processes to close the carbon budget [@Giering2014-tj; @Boyd2019-ez] and unkowns remain in the under-sampled mesopelagic (i.e. twilight) zone [@Martin2020-wa]. In order to fill the observational gaps, the Biogeochemical-Argo (BGC-Argo) network aims to develop an operational global array of 1000 profiling floats measuring six core variables from the surface to 2000 m [@Claustre2020-jo]: oxygen, nitrate, pH, chlorophyll a (Chla), suspended particles ($b_{bp}$) and downwelling irradiance. In addition to the six core variables, new sensors have been developped to target specific BCP-related questions [@Claustre2020-jo; @Claustre2021-tx; @Chai2020-uq]. In this study, we will focus on BGC-Argo floats equipped with two additional sensors: the Underwater Vision Profiler (UVP6) [@Picheral2021-sx] and a transmissometer used as an optical sediment trap (OST).

The UVP6 is a portable version of the UVP5 [@Picheral2010-to], specifically designed for AUVs [@Picheral2021-sx]. It consists of an underwater camera that counts particles and images objects in, respectively, the 0.1 - 2.5 cm and 0.8 - 2.5 cm size range. In contrast with UVP5 deployments on cabled platforms, UVP6 deployed on long-term drifting AUVs (e.g. BGC-Argo floats) are rarely recovered. Therefore, the latest version of the UVP6 also embarks an embedded image classification algorithm that transmits the abundance of 20 classes (16 biological classes) in near-real time. The OST consists of a vertically mounted transmissometer whose upward-facing optical window intercepts sinking particles. The latter have already been used on AUVs [@Bishop2004-at; @Bishop2009-ka; @Estapa2013-gw; @Estapa2017-jr; @Estapa2019-nk] and have demonstrated their usefulness to characterize the gravitational pump.

For the first time, two pairs of BGC-Argo floats equipped with both the UVP6 and an OST were deployed (May 2022) in the Labrador Sea (LS) to investigate the seasonal and episodic dynamics of particle and carbon fluxes. The LS is a basin of the subpolar North Atlantic (NA) ocean which represents 20% of the global ocean carbon sink \[@Takahashi2009-rv\]. The efficiency of this sink is explained by both deep winter convection that traps CO$_{2}$ from the atmosphere \[@Vage2008-qa; @Yashayaev2009-fe; @Yashayaev2017-mn\] and by the largest spring phytoplankton bloom \[@Siegel2002-hk\] that consumes CO$_{2}$ for the photosynthetic production of organic matter. The triggering mechanism of the NA bloom was initially explained by the 'Critical Depth Hypothesis' of @Sverdrup1953-ki that defines a critical surface mixing depth where phytoplankton growth is equal to phytoplankton losses. According to @Sverdrup1953-ki, a bloom is therefore triggered when the surface mixed layer depth (MLD) is shallower than this critical depth resulting in a positive phytoplankton growth rate. However, this hypothesis was challenged by @Behrenfeld2010-my who suggested that the initiation of the NA blooms begins in winter with a slow phytoplankton biomass increase over the following months (i.e. 'Dilution-Recoupling' hypothesis). These hypotheses have been investigated with BGC-Argo floats but the debate still remains \[@Mignot2018-gm; @Yang2020-hw; @Boss2010-do\]. For the LS, @Lacour2015-da used a climatology of satellite Chla to divide the NA into 6 bioregions with specific bloom phenologies. In their bioregionalization (see also their Figure 2), the LS is characterized by two bioregions with distinct bloom phenologies on both side of the 60°N parallel. The northern part is characterized by a short spring bloom in late April whereas the bloom in the southern part starts in April-May and slowly develops to reach its maximum in June. @Lacour2015-da concluded that the concurrent influence of surface light and mixing was the first-order mechanism controlling the onset of the spring bloom in both bioregions. This is coherent with the results of @Wu2008-vw and @Frajka-Williams2010-ph who found that early shoaling of the mixed layer was responsible for the early spring bloom in the northern part whereas the light controlled the bloom in the southern part.

In late May 2022, two pairs of BGC-Argo floats were deployed in the southern part of the LS at the time of the spring bloom. While BGC-Argo floats typically drift at 1000 m for \~10 days between each ascending profile, these two pairs of floats were configured to drift at three distinct parking depths (200 m, 500 m and 1000 m) to study POC and particle fluxes derived from beam attenuance \[@Estapa2023-oz\] and UVP6 particle size distributions (PSD). The goals of this study are threefold: 1) Compare the UVP6 and OST as two independent measurements of downward carbon fluxes and particle abundance; 2) Explore the seasonal signal of the downward POC flux and particle abundance with Chla and MLD using BGC-Argo floats and satellite data; 3) Evaluate the new drifting configuration and how it could be improved in regards with our preliminary results.

@@

parler aussi du fait que lesmesures en dérivés, il y a 2h en UVP et OST etc peut-etre que les mesures à 500 m ... ou alors on mets plus de temps à 200 m... voir un peu. faire des profils tous les 10 jours pour une telle apllication ça sert à rien étant donné qu'en plus si on a l'uvp 6 avec l ER embarquée pour éutider la vmmp il faut clairmeent avoir une résolution temporelle plus éleée, ce qui est loin parfait donc voilà.

TO DO - faire le profil de Martin (flux vertical) et faire les données de HPLC pour étudier les communautés et voir si elles sont différentes entre les deux sites de déploiements.
